Master Thesis

### 2013-06-11 the-last-part.tex
Working on introducing the first subtyping

>>>>

Our goal is to split the types into smaller parts that only talk about
features belonging to one of the three mechanisms covered above. This
means that we would like to take some phrase about which we know a lot
of disparate pieces of information (presence of negative determiner,
trace status, number\ldots), having type
e.g. $NP\_\textcolor{red}{NEG{=}T}\_\textcolor{green}{VAR{=}F}\_\textcolor{blue}{NUM{=}PL}$,
and use it as an argument for some function which only cares about one
channel of information and would have a type like
$NP\_\textcolor{red}{NEG{=}T} \limp N\_\textcolor{red}{NEG{=}F} \limp
N\_\textcolor{red}{NEG{=}T}$. To make a type such as
$NP\_\textcolor{red}{NEG{=}T}\_\textcolor{green}{VAR{=}F}\_\textcolor{blue}{NUM{=}PL}$
be a legal argument to a function which expects an argument of type
$NP\_\textcolor{red}{NEG{=}T}$, we will need to introduce some notion of
\emph{subtyping}.

The types we have been showing up to now propose a very straightforward
notion of subtyping. All of the types can be seen as conjunctions of
properties where $\_$ (underscore) is the conjunction operator. A type
$\tau$ can then be seen as a subtype of type $\sigma$ whenever the
conjuncts of $\tau$ form a superset of the conjuncts of $\sigma$. This
is not unlike the structural typing of records in OCaml (CITE SOME OCAML
SPEC HERE), where a record type is a subtype of another record type if
the former provides, among others, all the fields provided by the latter
and gives them the same type. In our case, one type is a subtype of
another if the former gives, among others, all the properties given by
the latter. This notion of subtyping can be expressed by adding the rule
of inference in Figure~\ref{fig:type-superset} to our type
system.\footnote{In the rule }

\begin{figure}
  \begin{prooftree}
    \AxiomC{$\Gamma_l; \Gamma_i \vdash_\Sigma M : A_1 \land \ldots A_{i-1} \land A_i \land A_{i+1} \ldots \land A_n$}
    \RightLabel{(subtype)}
    \UnaryInfC{$\Gamma_l; \Gamma_i \vdash_\Sigma M : A_1 \land \ldots A_{i-1} \land A_{i+1} \ldots \land A_n$}
  \end{prooftree}
  \caption{\label{fig:type-superset} A rule of inference giving us
    subtyping for conjunctions of atomic types. For readability, we use
    $\land$ instead of $\_$ (underscore) to designate the conjunction of
    properties.}
\end{figure}

With the new subtyping rule, we can

$$
S_{tatou} : N \land NEG{=}F \land NUM{=}SG
$$
$$
S_{le_{NEG_1}} : (N \land NEG{=}F) \limp (((NP \land NEG{=}F) \limp S) \limp S)
$$
$$
S_{le_{NEG_2}} : (N \land NEG{=}T) \limp (((NP \land NEG{=}T) \limp S) \limp S)
$$
$$
S_{le_{NUM}} : (N \land NUM{=}SG) \limp (((NP \land NEG{=}SG) \limp S) \limp S)
$$
$$
S_{le_{VAR}} : N \limp (((NP \land VAR{=}F) \limp S) \limp S)
$$
